### 2012-11-05 poster/poster.tex
Corrected comma - Edmund Jackson

Clojure is a recent and increasingly popular dynamically typed programming language.
Designed to be pragmatic, it is a dialect of Lisp supporting functional programming and immutability by default,
while being hosted on, and providing direct interoperability with popular platforms.
\end{posterbox}

>>>>

Clojure is a recent and increasingly popular dynamically typed programming language.
Designed to be pragmatic, it is a dialect of Lisp supporting functional programming and immutability by default,
while being hosted on, and providing direct interoperability with, popular platforms.
\end{posterbox}
